---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stylex

<!-- badges: start -->
<!-- badges: end -->

`stylex` is an R package to modify style setting in docx file. This is especially for Pandoc's docx input aka `reference.docx`. But any other docx file can be used.

## Installation

You can install the `stylex` package from [GitHub](https://github.com/niszet/stylex) with:

``` r
remotes::install_github("niszet/stylex")
# or
devtools::install_github("niszet/stylex")
```

## Example1


```{r example, eval=F}
library(stylex)

# set the complete file path
file = "sample.docx"

# get xml object from style.xml in the target docx
xml <- read_style_xml(file)

# extract style tags from xml object of style.xml
style_xml <- get_style_tags(xml)

# transform to data.frame by style_xml object.
d <- style2df(style_xml)

# try to modify by specifing style_id and column name.
d[d$style_id=="1","r_sz_val"] <- "400"

# update xml file by updated data.frame with original docx file.
xml <- update_xml(file, d)

# write the modified docx file.
write_style(xml, file, "modified.docx")
```

## Example2

Internally, `stylex` package uses functions to each tags in docx file. Users can use these functions by calling with `:::` because these are internal functions.


```{r example2, eval=F}
library(stylex)

file = "sample.docx"
xml <- read_style_xml(file)
style_xml <- get_style_tags(xml)

# node extract by tag name of "Date".
node <- get_node_by_name(style_xml, "Date")

# users can identify the node by style_id.
# This is more adequate because id is unique in the docx.
# node <- get_node_by_id(style_xml, "1")

# by name, you must write that exactly, i.e. white spaces.
# node <- get_node_by_name(style_xml, "heading 5")

# Because the node is an object of xml2, prior to View it load xml2 package.
# library(xml2)
# View(node)

# set the value by each functions to each tags.
# when node object changes, original xml object is also changed.
stylex:::set_r_sz_val(node, "42")
stylex:::set_r_color_themecolor(node, "accent2")
stylex:::set_p_spacing_before(node, 2000)
stylex:::set_r_b(node, T)

write_style(xml, file, "modified.docx")

```
